Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Show example XML code, use to explain instancing

>>>>

The XML below shows how the second pass of the first approach is rendered.
Notice that the render graph supports basic instancing through the {\em group}
and {\em instance} nodes.  When an instance node is visited, it simply traverses
the group it points to.  Complex behavior can be achieved with nested groups.

\begin{Verbatim}[fontsize=\small]
  <cull faces="front" />
  <framebuffer>
    <attachment usage="color" link="coords-texture-1" />
    <use program="primary-coords-program">
      <group id="intersection-group">
        <booleanAnd of="cube-1 cube-2" />
      </group>
    </use>
  </framebuffer>
  <framebuffer>
    <attachment usage="color" link="coords-texture-2" />
    <use program="secondary-coords-program">
      <instance of="intersection-group" />
    </use>
  </framebuffer>
  <cull faces="back" />
  <framebuffer>
    <attachment usage="color" link="results-texture" />
    <use program="second-pass-program">
      <uniform name="CoordsTexture1" link="coords-texture-1" />
      <uniform name="CoordsTexture2" link="coords-texture-2" />
      <uniform name="VolumeTexture1" link="volume-texture-1" />
      <uniform name="VolumeTexture2" link="volume-texture-2" />
      <uniform name="MVPMatrix" usage="modelviewprojection" />
      <instance of="intersection-group" />
    </use>
  </framebuffer>
\end{Verbatim}
